SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization

### 2014-04-29 paper/paper.tex
paper: draft notice.
paper: wibbles, grab latest graphs.

\title{SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization}
%\subtitle{Subtitle Text, if any}

@@

\begin{figure}[ht]
\includegraphics[scale=0.6]{Graphs/data}
\includegraphics[scale=0.6]{Graphs/time-big}
\includegraphics[scale=0.6]{Graphs/time-small}
  \caption{Results for 2000 tests of the program in Figure~\ref{fig:initial}.}
  \label{fig:graphs}
\end{figure}

@@

  \item \emph{Heap}, an example from the QuickCheck test suite, in which an
    incorrect ``to sorted list'' function is checked.
\end{itemize}

\noindent
All benchmarks can be found at
\url{https://github.com/leepike/SmartCheck/tree/master/regression}.  Benchmarks
are against QuickCheck~2.7.   The benchmarks only compare the size of shrunk
values and the time required to generate them using standard arguments to
QuickCheck and SmartCheck.  We do not benchmark the generalization algorithms,
since there is no analog in QuickCheck  or other testing frameworks.

>>>>

\title{SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization}
\subtitle{UNPUBLISHED DRAFT}

@@

\begin{figure}[ht]
\includegraphics[scale=0.6]{../regression/PaperExample1/out/data}
\includegraphics[scale=0.6]{../regression/PaperExample1/out/time-big}
\includegraphics[scale=0.6]{../regression/PaperExample1/out/time-small}
  \caption{Results for 2000 tests of the program in Figure~\ref{fig:initial}.}
  \label{fig:graphs}
\end{figure}

@@

  \item \emph{Heap}, an example from the QuickCheck test suite, in which an
    incorrect ``to sorted list'' function is checked.

  \item \emph{Parser}, a parser/pretty-printer for a toy imperative language
    containing a parser bug that switches the arguments of an binary operator.
\end{itemize}

\noindent
All benchmarks can be found at
\url{https://github.com/leepike/SmartCheck/tree/master/regression}.  Benchmarks
are against
QuickCheck~2.7.3.\footnote{\url{http://hackage.haskell.org/package/QuickCheck-2.7.3}}
The benchmarks only compare the size of shrunk values and the time required to
generate them using standard arguments to QuickCheck and SmartCheck.  We do not
benchmark the generalization algorithms, since there is no analog in QuickCheck
or other testing frameworks.
